Untitled

### 2019-12-17 analysis/analysis_fe.Rmd

```{r}
library(tidyverse)
library(readr)
fe <- read_xlsx("experiment-export.xlsx", sheet=2) %>%
  filter(!is.na(contributor)) %>%
  mutate(contributor = factor(contributor))
```

>>>>

```{r}
library(tidyverse)
library(readxl)
fe <- read_xlsx("experiment-export.xlsx", sheet=2) %>%
  filter(!is.na(contributor)) %>%
  mutate(contributor = factor(contributor))
```
